### 2023-12-21 manuscript.tex
Update manuscript.tex

Three models were constructed in response to the three research questions mentioned above:  the daughter model, the continuance model and the persistence model.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.  Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance and intention of genitally cutting daughters.  We used the two structural models to further understand how such positions change the main model.

@@

Co-variables in the models were basic social demographic variables (country, gender awareness, education, media, job, residence (rural vs. urban), religion, marital status, age, and wealth).  We also included gender awareness (see — for questions of gender awareness proxy) in our models to test if women’s gender awareness would associate with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.  Cluster ID (villages) and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it) were treated as random variables.  We treated ethnicity as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.

Regarding potential community impact on the practice of FGC, the models also teated education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.

In addition, daughter fgc plan at a group level was added to daughter model; persistence at a group level to persistence model; and daughter fgc plan at a group level, persistence and persistence at a group level to mixed model.  Media use and gender awareness were also scored.

>>>>

Three models were constructed in response to the three research questions mentioned above:  the daughter model, the continuance model and the persistence model.  The main one is the “daughter” model, which analyzed associations of beliefs of FGC benefits (see the list of FGC benefits at table xx) and behavioral intention to have their daughters receiving FGC.  Additionally, we decomposed the model into two “structural” models:  structural one “continuance” model to study women’s beliefs of FGC benefits and FGC continuance; and structural two “persistence”  model \cf{or “mixed” model?} to examine the association of beliefs of FGC benefits, FGC continuance on intention of genitally cutting daughters.  We used the two structural models to further understand how such positions change the main model.

@@

Co-variables in the models were basic social demographic factors (i.e., country, education, job, residence (rural vs. urban), religion, marital status, age, media use, and wealth) in addition to gender awareness.  Gender awareness (see — for questions of gender awareness proxy) was included to test if women’s gender awareness interacted with their intention of cutting daughters’ genitals and their position of FGC practice overall \cfonly{cite{Dell04, FrieMahm13,KhosBane17, Lewi95, Lewi09, Meye00, Morr08, Njam04, UNIC16, YirgKass12, Youn02} check and cut}.  Media use and gender awareness were scored.  Cluster ID (i.e., villages where the samples were from) and ethnicity (see the list of ethnicity recode at table xx in appendix) \cfonly{with a footnote on how we recoded it} were treated as random variables.  Ethnicity was applied as a random effect based on previous study which showed little differences in results using individual rather than cluster ethnicity \cite{Hayf05}.

Regarding potential community impact on the practice of FGC, mothers' intention on having FGC on daughters, FGC continuance, and FGC beliefs. The following also tested at a community level:  education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level \cfcmt{on a cluster level, not national, right?} with cluster as a proxy to represent a community level of impact \cite{AligRen06, BoylSvec19, Hayf05, Krav02}.
